How Tree-like are the data?

### 2019-04-12 phylotreelike.rmd
need to ggplot the figures

Can we get away with just sampling traits from the tree?

@@

Here I sample 10,000 points from the n-dimension space using a MVN with the phylogenetic variance. 
It is surprising how fast it levels off.

@@

```{r increasing traits, echo=FALSE,cache=TRUE,eval=FALSE}

@@

plot(dd2$line,dd2$LRT)
plot(dd2$line,dd2$sumLRT)

@@

Just a exteme example, what if we combine a bunch of non-tree-like traits? 
By ordering the

>>>>

Can we get away with just sampling traits from the tree? (Yes!)

@@

```{r ggprop, echo=FALSE}

ggprop <- (ggplot(ddprop, aes(x=nspp,y=prop))
  + geom_point()
  + geom_line()
  + theme_bw()
  + ylab("Proportion of Tree-like traits")
  + xlab("Number of species")
)

print(ggprop)

Here I sample 10,000 points from the n-dimension space using a MVN with the phylogenetic variance. 
It is surprising how fast it levels off.
TODO: Maybe add confidence interval bands.

@@

```{r increasing traits, echo=FALSE,cache=TRUE,warning=FALSE}

@@

# plot(dd2$line,dd2$LRT)

gg1 <- (ggplot(dd2, aes(x=line, y=LRT))
  + geom_point()
  + theme_bw()
  + ylab("Tree like")
  + xlab("Trait")
)

print(gg1)

dd3 <- dd2 %>% gather(key = "tip", value = "obs", -c(line,ll,null,LR,sumLL,sumnull,LRT,sumLR,sumLRT))

gg2 <- (ggplot(data=(dd3 %>% filter(line<50)), aes(x=tip, y=obs, color=tip,group=line,alpha=LRT))
  + geom_point()
  + geom_line()
  + theme_bw()
  + scale_color_manual(values=c("black","red","blue"))
  + ylab("observed measurements")
)

print(gg2)

gg3 <- (ggplot(data=(dd3 %>% filter(line<15)), aes(x=tip, y=obs, color=tip,group=line,alpha=sumLRT))
  + geom_point()
  + geom_line()
  + theme_bw()
  + scale_color_manual(values=c("black","red","blue"))
  + ylab("observed measurements")
)

print(gg3)

plot(dd2$line,dd2$sumLRT)

@@

Just a exteme example, what if we combine a bunch of non-tree-like traits?
